---
title: "Create function and adapt structure"
author: "Erwan"
date: 2021-11-30
categories: ["R"]
tags: ["tmtcbythecc"]
---

How to code ? 
package::function 

usethis:unsepackage(package3) pour rajouter package3 au fichier DESCRIPTION 

Now you are suppose to have a beautiful project structure link to gitHub. Now that we finished to create the basis of the project we will start it ! We will beging by creat a new function. 

To do so we will create a new script. As we said we will use the R file to put inside R scripts that construct functions. The name of the script is really important, we will call it 01_clean_data_function.R. Each script that create function will finish by "function". We will create a function to clean the dataset.  


We open 01_clean_data_function.R and we write : 

```{r, eval=FALSE}
pokeclean <- function(poke){
  poke2 <- poke[-poke$generation %in% c("4", "5", "6", "7"), ]
  poke3 <- poke2[,-which(names(poke2) %in% c("japanese_name","classfication"))]
  return(poke3)
}
```

```{r, eval=FALSE, echo=FALSE}
poke <- read.csv("~/Desktop/PHD1/Formation/Reproductibility/PokeRepro/data/pokemon.csv")
```

voila  voila 

When you create a function you also have to create a header Roxygene

-on creer une function dans le dossier R “01_clean_data_function”
-dans analysis on creer “01_clean_data.R”

-on creer une function dans le dossier R “02_??_function.R”
-dans analysis on creer “02_???.R”

-dans analysis on creer “03_which_type.R” 
-dans ouputs on creer “03_which_type_barplot.png”  
-dans ouputs on creer “03_which_type_camemmbert.png”  
 
-dans analysis on creer “04_regression_weight_attack.R” 
-dans ouputs on creer “04_regression_weight_attack.png” 
-dans ouputs on creer “04_regression_weight_attack.RDATA”

